\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2021-02-14 iros-2021.tex
cleaning
late night fixes

%% references (generates a bib file for bibtex)
\begin{filecontents}{\jobname.bib}
  @inproceedings{seewald2020mechanical,
    title={Mechanical and Computational Energy Estimation of a Fixed-Wing Drone}, 
    author={Seewald, Adam and Garcia de Marina, Hector and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
    booktitle={2020 Fourth IEEE International Conference on Robotic Computing (IRC)},
    pages={135--142},
    year={2020},
    organization={IEEE},
    DOI={10.1109/IRC.2020.00028},
    url={https://adamseew.bitbucket.io/short/mechanical2020}
  }

@@

    url={https://adamseew.bitbucket.io/short/coarse2019}

@@

    url={https://adamseew.bitbucket.io/short/component2019}

@@

    url={https://adamseew.bitbucket.io/short/energy2020}

@@

    url={https://adamseew.bitbucket.io/short/beyond2020}

@@

\begin{figure}[h!]
  \footnotesize
  \input{\figpath/results/new_physics/trajs.tikz}
  \caption[Path of a static and dynamic plan]{Path simulations with variations of wind speed and direction. In I, II the path is static. It is dynamically adapted with the algorithm in I.d, with the path parameter radius of the circle $c_1$ and computation parameter frames-per-second rate $c_2$}
  \label{fig:trajs}
\end{figure}
\begin{figure}[h!]
  \footnotesize
  \input{\figpath/results/new_physics/model.tikz}
  \caption[Energy estimation and evolution of the state]{Energy estimation process for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right}
  \label{fig:model}
\end{figure}
\begin{figure}[h!]
  \footnotesize
  \input{\figpath/results/new_physics/ener.tikz}
  \caption[] {The model after 200 seconds of estimation on top along the energy and the algorithm that dynamically adapts path when the UAV cannot reach the end of the plan, and adapts the computation when the battery is discharged (smaller plot on right)}
  \label{fig:ener}
\end{figure}

>>>>

%% references (generates a bib file for bibtex)
\begin{filecontents}{\jobname.bib}
  @inproceedings{seewald2020mechanical,
    title={Mechanical and Computational Energy Estimation of a Fixed-Wing Drone}, 
    author={Seewald, Adam and Garcia de Marina, Hector and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
    booktitle={2020 Fourth IEEE International Conference on Robotic Computing (IRC)},
    pages={135--142},
    year={2020},
    organization={IEEE},
    DOI={10.1109/IRC.2020.00028},
    url={https://adamseewald.cc/short/mechanical2020}
  }

@@

    url={https://adamseewald.cc/short/coarse2019}

@@

    url={https://adamseewald.cc/short/component2019}

@@

    url={https://adamseewald.cc/short/energy2020}

@@

    url={https://adamseewald.cc/short/beyond2020}

@@

\begin{figure}[ht]
  \footnotesize
  \input{\figpath/results/new_physics/trajs.tikz}
  \caption[Path of a static and dynamic plan]{Path simulations with variations of wind speed and direction. In I, II the path is static. It is dynamically adapted with the algorithm in I.d, with the path parameter radius of the circle $c_1$ and computation parameter frames-per-second rate $c_2$}
  \label{fig:trajs}
\end{figure}
\begin{figure}[ht]
  \footnotesize
  \input{\figpath/results/new_physics/model.tikz}
  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right}
  \label{fig:model}
\end{figure}
\begin{figure}[ht]
  \footnotesize
  \input{\figpath/results/new_physics/ener.tikz}
  \caption[] {The models after 200 seconds on top. The algorithm that uses the model I to dynamically adapt the path (when the final time and battery time doesn't match) and the computation (when the battery is discharged--the smaller plot on right) on bottom}
  \label{fig:ener}
\end{figure}
